A unified model for parsing and sentence understanding

### 2016-03-13 writing/hard_stack_paper/paper.tex
More paper content.

This feature vector is then passed to a series of two (\todo{Update w/ final number}) ReLU neural network layers, then passed into a linear transformation, and then finally passed to a softmax layer, which yields a distribution among the three labels.

@@

The use of a probabilistic classifier is simply a convenience for training. Transition decisions are hard, and only a single transition is chosen at each step (i.e., it is not well defined in our model to perform only three-quarters of a \shift operation).

@@

We evaluate five models on the SNLI task. Each uses 300d hidden states: \todo{[SB] Reframe around M1.}
\begin{itemize}
\item A baseline LSTM model (similar to that of \citealt{snli:emnlp2015}) that uses the same classifier architecture as our models, but encodes sentences using a single layer LSTM RNN sequence model.
\item The unaugmented transition-based sentence model.
\item The transition-based sentence model with the tracking LSTM.
\end{itemize}

\todo{[SB] Describe metrics, esp parsing.}

\begin{table*}[t]
  \centering\small
  \begin{tabular}{lcccc} 
    \toprule
Model                   & Params.    & Trans. acc.  &   Train  &   Test \\
\midrule
\multicolumn{4}{c}{Previous non-NN results}\\
\midrule
Lexicalized classifier \cite{snli:emnlp2015}
                        & --                & --                    &   99.7   &   78.2      \\
\midrule
\multicolumn{4}{c}{Previous sentence encoder-based NN results}\\
\midrule
100d LSTM encoders \cite{snli:emnlp2015}
                        & 221k               & --               &   84.8   &   77.6      \\
1024d pretrained GRU encoders \cite{DBLP:journals/corr/VendrovKFU15}
                        & 15m                & --              &   98.8   &   81.4       \\
300d Tree-based CNN encoders \cite{mou2015recognizing}
                        & 3.5m                & --             &   83.4   &   82.1       \\
\midrule
\multicolumn{4}{c}{Other previous NN results}\\
\midrule
100d LSTM w/ word-by-word attention \cite{rocktaschel2015reasoning}
                        & 252k               & --              &   85.3   &   83.5       \\
300d mLSTM word-by-word attention model \cite{DBLP:journals/corr/WangJ15b}
                        & 1.9m               & --             &   92.0   &   86.1      \\
300d LSTMN with deep attention fusion \cite{cheng2016long}
                        & 1.4m               & --                &   92.3   &   \textbf{89.1}      \\
\midrule
\multicolumn{4}{c}{New results}\\
\midrule
\result{300d LSTM RNN } & ?                  & --                &   83.9      &   80.6       \\
\result{300d PINN-Ext w/o tracking}   
                        & ?                  & --                &   ?      &   81.9dv       \\
\result{300d PINN-Ext }
                        & ?                  & --                &   ?      &   \underline{84.8dv}       \\
\result{300d PINN }
                        & ?                  & 92.2+dv                  &   ?    &   83.3+dv       \\          
% \result{300d PINN-Ext, sequence-based attn.   }     
%                         & ?                  & --                &   ?      &   86.3dv         \\
% \result{300d PINN-Ext, tree-based attn. }           
%                         & ?                  & --                &   ?      &   \textbf{?}\\
    \bottomrule
  \end{tabular}
  \protect\caption{\protect\label{tab:results}Results on SNLI 3-way inference classification. Params. is the approximate number of trained parameters (excluding word embeddings for models where they are trained). Trans. acc. is the model's accuracy in predicting parsing transitions. Train and test are SNLI classification accuracy. \result{[JG]Add seconds-per-step *if* we get a reasonably well-optimized model in time.} \todo{[SB]: Estimate param counts.}} 
\end{table*}

\paragraph{Results}

Table~\ref{tab:results} shows our results.

@@

Implementing such a model on top of our proposed stack-based design would learn a model that could productively share representations between the two tasks. Implementing such a model on top of a differentiable version of our stack-based design (possibly following \citealt{grefenstette2015learning,joulin2015inferring}) would further make it possible for the model to learn to parse using guidance from the semantic representation objective, essentially allowing  learn to produce parses that are, in aggregate, better suited to supporting semantic interpretation than those supplied in the training data.

>>>>

This feature vector is then passed to a series of two (\todo{Update w/ final number}) ReLU neural network layers (following \citealt{snli:emnlp2015}), then passed into a linear transformation, and then finally passed to a softmax layer, which yields a distribution among the three labels.

@@

The use of a probabilistic classifier is simply a convenience for training. Transition decisions are hard, and only a single transition is chosen at each step (i.e., it is not well defined in our model to perform only three-quarters of a \shift operation). Because of this, the transition prediction function is trained solely using a parsing-related objective, and cannot be directly trained to optimize for the downstream semantic objective, even though it uses the same word and phrase representations that are used for that downstream objective. We leave the project of true joint learning---learning syntactic parsing from a semantic objective---to future work.

@@

We evaluate four models on the SNLI task. Each uses 300d hidden states:
\begin{itemize}
\item A baseline LSTM model (similar to that of \citealt{snli:emnlp2015}) that uses the same classifier architecture as our models, but encodes sentences using a single layer LSTM RNN sequence model.
\item The minimal PINN-Ext model, which uses transitions from an external parser, and has no tracking LSTM to inform semantic composition. This model is strictly equivalent to a TreeLSTM.
\item The full PINN-Ext model, which adds in the use of a tracking LSTM to guide composition, making it a tree-sequence hybrid.
\item The full PINN model, which makes its own parsing decisions, and does not depend on an external parser at test time, making it slightly weaker but a practical choice in applied settings.
\end{itemize}

We compare our models against a range of baselines, including the strongest published non-neural network-based result from \cite{snli:emnlp2015}, a set of previous neural network models built around sentence encoders, and a set of models built around soft attention architectures. We should note that these attention-based models are by far the strongest published on SNLI to date, but we do not wish to compare our model with those models directly. SNLI was originally presented as an evaluation and development task for sentence encoding models, on the premise that sentence encoding models that do well on SNLI capture sentence meaning in a general sense, and are well suited to use on a range of NLP tasks. We follow that approach, and focus on sentence encoding, rather than on attentional models, which are much more narrowly adapted to the sentence-pair structure of SNLI examples.

\begin{table*}[t]
  \centering\small
  \begin{tabular}{lcccc} 
    \toprule
Model                   & Params.    & Trans. acc.  &   Train  &   Test \\
\midrule
\multicolumn{5}{c}{Previous non-NN results}\\
\midrule
Lexicalized classifier \cite{snli:emnlp2015}
                        & --                & --                    &   99.7   &   78.2      \\
\midrule
\multicolumn{5}{c}{Previous sentence encoder-based NN results}\\
\midrule
100d LSTM encoders \cite{snli:emnlp2015}
                        & 221k               & --               &   84.8   &   77.6      \\
1024d pretrained GRU encoders \cite{DBLP:journals/corr/VendrovKFU15}
                        & 15m                & --              &   98.8   &   81.4       \\
300d Tree-based CNN encoders \cite{mou2015recognizing}
                        & 3.5m                & --             &   83.4   &   82.1       \\
\midrule
\multicolumn{5}{c}{Our results}\\
\midrule
300d LSTM RNN encoders          & 1.7m                  & --                &   83.9      &   80.6       \\
\result{300d PINN-Ext w/o tracking}   
                        & ?                  & --                &   ?      &   81.9dv       \\
\result{300d PINN-Ext }
                        & ?                  & --                &   ?      &   \underline{84.8dv}       \\
\result{300d PINN }
                        & ?                  & 92.2+dv            &   ?    &   83.3+dv       \\          
% \result{300d PINN-Ext, sequence-based attn.   }     
%                         & ?                  & --                &   ?      &   86.3dv         \\
% \result{300d PINN-Ext, tree-based attn. }           
%                         & ?                  & --                &   ?      &   \textbf{?}\\
\midrule
\multicolumn{5}{c}{Other previous NN results}\\
\midrule
100d LSTM w/ word-by-word attention \cite{rocktaschel2015reasoning}
                        & 252k               & --              &   85.3   &   83.5       \\
300d mLSTM word-by-word attention model \cite{DBLP:journals/corr/WangJ15b}
                        & 1.9m               & --             &   92.0   &   86.1      \\
300d LSTMN with deep attention fusion \cite{cheng2016long}
                        & 1.4m               & --                &   92.3   &   \textbf{89.1}      \\
    \bottomrule
  \end{tabular}
  \protect\caption{\protect\label{tab:results}Results on SNLI 3-way inference classification. Params. is the approximate number of trained parameters (excluding word embeddings for models where they are trained). Trans. acc. is the model's accuracy in predicting parsing transitions. Train and test are SNLI classification accuracy. \todo{[SB]: Estimate param counts as numbers come in.}} 
\end{table*}

\paragraph{Results} Table~\ref{tab:results} shows our results. Our primary evaluation metric for all models is three-way classification accuracy on the SNLI test set. For the full PINN model, we also report a measure of the agreement of its generated parses with the Stanford Parser's parses of the same data, expressed in terms of the model's accuracy in making two-way transition decisions. In addition, we report the number of trained parameters in each model as well as training set accuracy.

We find that the bare PINN-Ext model performs relatively poorly, but that the full PINN-Ext with the added tracking LSTM reaches state-of-the-art accuracy among sentence encoding based models, indicating that our tree-sequence hybrid approach succeeds in combining the strengths of both approaches to encoding. The fully independent PINN model with its relatively weak internal parser performs more poorly, but nonetheless exceeds the performance of the LSTM baseline. None of our models reached the performance of the strongest attention-based models, which were explicitly engineered for the sentence pair-based structure of the SNLI task.

@@

For a more ambitious goal, we expect that it should be possible to implement a variant of the PINN on top of a modified stack data structure with differentiable \textsc{push} and \textsc{pop} operations (possibly following \citealt{grefenstette2015learning,joulin2015inferring}) would make it possible for the model to learn to parse using guidance from the semantic representation objective, essentially allowing learn to produce parses that are, in aggregate, better suited to supporting semantic interpretation than those supplied in the training data.
